Data exploration through dot-driven development\footnote{This work was supported by The Alan Turing Institute under the EPSRC grant EP/N510129/1 and by the Google Digital News Initiative.}

### 2017-04-12 ecoop-2017/paper.tex
Organize papers

\title{Data exploration through dot-driven development\footnote{This 
  work was supported by Google Digital News Initiative.}}
\titlerunning{Data exploration through dot-driven development}

>>>>

\title{Data exploration through dot-driven development\footnote{This 
  work was supported by The Alan Turing Institute under the EPSRC grant EP/N510129/1
  and by the Google Digital News Initiative.}}
\titlerunning{Data exploration through dot-driven development}
